Our Future Nuclear Data Needs

### 2018-12-19 nuclear_data_needs/nuclear_data_needs.tex
Added reference for Batch's forthcoming Cl(n,p) Phys Rev C

\begin{figure}[b]
 \centering
%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
 \includegraphics[width=0.7\linewidth]{rotated_swings.pdf}

@@

\begin{figure}[t]
 \centering
%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
 \includegraphics[width=0.6\linewidth]{239pu_nn_cropped.pdf}

@@

Recent results from activation using a DD-neutron source \cite{Voyles2017} indicate both resonant behavior in this cross section and an average value significantly smaller value for  $2.2 < E_n \text{(MeV)} < 2.7$ \textred{\cite{Bat18}}.  

>>>>

\begin{figure}
 \centering
%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
 \includegraphics[width=0.7\linewidth]{rotated_swings.pdf}

@@

\begin{figure}
 \centering
%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
 \includegraphics[width=0.6\linewidth]{239pu_nn_cropped.pdf}

@@

Recent results from activation using a DD-neutron source \cite{Voyles2017} indicate both resonant behavior in this cross section and an average value significantly smaller value for  $2.2 < E_n \text{(MeV)} < 2.7$ \cite{Bat18}.  
